A User-Centric Approach to the Design and Consequences of Recommender Systems

### 2019-12-14 paper/www20-rebuttal.txt

[Review1and2]: We focused on building a model based on assumptions backed by work in psychology and economic decision theory. An online experiment with real users is a great idea and will be addressed in future work.
Clarity issues will be addressed in the revision.

[Review2Q1]: At the start V_i and V are drawn for each product and individual so that realized value (and utility) of each item is fixed throughout. Each user has correct initial beliefs about the distribution these are drawn from, a standard assumption in decision theory. As the user observes realized values of items they consume (x_{i,n}'s), they update beliefs on the distribution of values of the remaining items. The reason this updating is meaningful is that these values are correlated. The crucial point is that there is a difference between the perceived ("ex-ante") expected utility driving users’ decisions and the true/realized ("ex-post") utility. The user’s decisions depend on how much they know about the items, but the realized utility does not.

The realized X_i(=V_i+\beta*V) is fixed, only uncovered upon consumption. Without recommendation, user's beliefs are a combination of uncertainty over V and V_i. Recommendation reveals the realized V, but does not affect uncertainty over V_i.

Realized utility is fixed throughout so oracle recommendation does not need to account for user beliefs.

[Review2Q2]: We should have and will provide references from decision theory. We use a standard formulation of risk preferences, CARA preferences. The certainty equivalent of an item is homeomorphic to its expected utility, where risk attitudes play a role. The certainty equivalent of an item is the certain value x (line 248) that leads to the same expected utility: u(x)=E[u(item)]. As such, it is sufficient to know the certainty equivalents to which items have highest expected utility. In a Gaussian environment with CARA preferences, the expected utility of an item is increasing in mean and decreasing in variance (line 313), capturing users’ dislike of uncertainty. Higher risk aversion implies a higher penalty to uncertainty when ranking items. In our setup, having explored more nearby items decreases uncertainty, which may lead consumers to prefer safer items with lower expected values over riskier items with higher means.

[Review2Q3]: The illustrative example is under-specified as the arguments hold for any variance: information on item 0’s value impacts beliefs about both mean and variance and, under risk-aversion, both are relevant in determining user’s choices. Omitted algebraic details provided in the revision.

[Review2Q4]: We suppose the recommender knows V at t=0 and does not need to learn them. Having the recommender also learning V is an interesting extension, worth studying.

[Review3]: Existing approaches to serendipity and diversity focus on predicting realized utilities and "diversifying" the recommended itemset. Our approach emphasizes the role of beliefs and using as an evaluation metric the recommendation’s impact on user behavior.

### 2019-12-14 paper/filter_bubbles.tex
add rebuttal, WINE poster, and fix typos

% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
\copyrightyear{2020}
\acmYear{2020}
\setcopyright{acmlicensed}
\acmConference[WWW'20]{Recomme '18: ACM Symposium on Neural Gaze Detection}{April 20-24, 2020}{Taipai, Taiwan}
\acmBooktitle{RecSys '19: ACM Conference on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmDOI{10.1145/1122445.1122456}
\acmISBN{978-1-4503-9999-9/18/06}

@@

\textbf{Our Model and Contributions} In this paper, 
%drawing from recent work in psychology and decision theory in economics, 
we first propose a model of consumer decision-making in the context of large choice sets faced by users in online markets and show that the model is able to rationalize features of user behavior in such contexts by means of simulations. 
We then ask how a stylized model of recommendation can shape the behavior of long-lived users
and finally ask how the insights from our model can be used to improve recommender system design and to better understand the consequences of these systems.
\par

The key components of our model are:
\begin{enumerate}[label=(\arabic*)]
\item Users face uncertainty about their valuation of the different goods and thus face a decision problem under under uncertainty.
\item Choice sets are large and users only consume a small fraction of this choice set over their lifetime.
\item Consumption of these items is sequential and users live for multiple periods.
\item Consuming an item provides information about the value of similar items in the product space.
\item Recommendation provides users with information, reducing their uncertainty.
\end{enumerate}

@@

First, the bottom panel of Figure \ref{fig:correlation_consumption_path} shows that, when $\rho = 0$, there is no difference in consumption distance between the three regimes. This is due to the fact that when $\rho = 0$, there is no reason that items that are close in the product space should have similar va;ues and so the optimal consumption path does not depend on the similarity of the items. However this also means that users do not learn anything about neighboring products and so there is limited path-dependence in consumption.
\par

>>>>

% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
\copyrightyear{2020}
\acmYear{2020}
\setcopyright{acmlicensed}
\acmConference[WWW'20]{Recomme '18: ACM Symposium on Neural Gaze Detection}{April 20-24, 2020}{Taipei, Taiwan}
\acmBooktitle{RecSys '19: ACM Conference on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmDOI{10.1145/1122445.1122456}
\acmISBN{978-1-4503-9999-9/18/06}

@@

\noindent \textbf{Our Model and Contributions} In this paper, 
%drawing from recent work in psychology and decision theory in economics, 
we first propose a model of consumer decision-making in the context of large choice sets faced by users in online markets and show that the model is able to rationalize features of user behavior in such contexts by means of simulations. 
We then ask how a stylized model of recommendation can shape the behavior of long-lived users
and finally ask how the insights from our model can be used to improve recommender system design and to better understand the consequences of these systems.
\par

The key components of our model are:
\begin{enumerate}[label=(\arabic*)]
\item Users face uncertainty about their valuation of the different goods and thus face a decision problem under uncertainty.
\item Choice sets are large and users only consume a small fraction of this choice set over their lifetime.
\item Consumption of these items is sequential and users live for multiple periods.
\item Consuming an item provides information about the value of similar items in the product space.
\item Recommendation provides users with information, reducing their uncertainty.
\end{enumerate}

@@

First, the bottom panel of Figure \ref{fig:correlation_consumption_path} shows that, when $\rho = 0$, there is no difference in consumption distance between the three regimes. This is due to the fact that when $\rho = 0$, there is no reason that items that are close in the product space should have similar values and so the optimal consumption path does not depend on the similarity of the items. However this also means that users do not learn anything about neighboring products and so there is limited path-dependence in consumption.
\par
